### 2021-04-22 input/figproof.tex
some spacing and figure placement

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$ messages may
      stop other $\alpha$ messages from reaching all \processes ($b$
      and $c$) that require it along the shortest path. Consistent
      partitioning requires eventual purging of stale messages (see
      Figure~\ref{fig:proofB}).]  {\input{input/figproofA.tex}}
    \hspace{10pt}
    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$ messages may
      stop $\delta$ messages from reaching processes with the corresponding
      partition. Consistent partitioning requires that all \processes propagate
      $\delta$ messages as often as possible (I'); detect possible inconsistencies
      when parents' $\alpha$ messages contradict delivery history (III); notify
      processes of possible inconsistencies (IV).]
    {\input{input/figproofB.tex}}
    \caption{\label{fig:proof}Concurrent operations,
      delivery orders, and stale control information may impair
      consistent partitioning. Dynamic consistent partitioning
      requires eventual purging of stale messages, and best eventual
      forwarding.}
  \end{center}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$ messages may
      stop other $\alpha$ messages from reaching all \processes ($b$
      and $c$) that require it along the shortest path. Consistent
      partitioning requires eventual purging of stale messages (see
      Figure~\ref{fig:proofB}).]  {\input{input/figproofA.tex}}
    \hspace{10pt}
    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$ messages may
      stop $\delta$ messages from reaching processes with the corresponding
      partition. Consistent partitioning requires that all \processes propagate
      $\delta$ messages as often as possible (I'); detect possible inconsistencies
      when parents' $\alpha$ messages contradict history or state (III); notify
      processes of possible inconsistencies (IV).]
    {\input{input/figproofB.tex}}
    \caption{\label{fig:proof}Concurrent operations,
      delivery orders, and stale control information may impair
      consistent partitioning. Dynamic consistent partitioning
      requires eventual purging of stale messages, and best eventual
      forwarding.}
  \end{center}
\end{figure*}
